# Week 4 Short Answer Questions

## Ruotong Wang 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

**Problem 8.1**
1) ggplot()
2)geom_point(),geom_histogram(),geom_segment()
3)ylab(),xlim()
4)facet_wrap()
5)scale_y_kog10()

**Problem 8.2**
(1)
```{r}
ggplot(data=mosaicData::CPS85,aes(x=age,y=wage,shape=married))+geom_point()+facet_wrap(~sector, ncol = 3)
```
(2)
```{r}
ggplot(data=mosaicData::CPS85,aes(x=age,y=wage))+geom_point()+facet_wrap(~sex+married, ncol = 2)
```

**Problem 8.3**
(A)
```{r}
ggplot(data=mosaicData::CPS85,aes(x=age,y=wage))+geom_point()
```
(B)
```{r}
ggplot(data=mosaicData::CPS85,aes(x=age,y=wage,shape=sex))+geom_point(show.legend = TRUE)
```
(C)
```{r}
ggplot(data=mosaicData::CPS85,aes(x=age,y=wage,shape=sex))+geom_point(show.legend = TRUE)+facet_wrap(~married, nrow = 2)
```
(D)
```{r}
ggplot(data=mosaicData::CPS85,aes(x=age,y=wage,shape=married))+geom_point(show.legend = TRUE)
```

**Problem 9.1**
*str() is a quick presentation 
*group_by is a data verb 
*rank() is a transformation 
*mean() is a summary function 
*filter() is a data verb
*summary() is a quick presentaiton 
*summarise() is a data verb 
*anti_join() is a data verb
*glimpse() is a quick presentation

**Problem 9.3**

*Task 1
```{r}
diamonds %>%
  group_by(color) %>%
  summarize(ave=mean(carat, na.rm=TRUE)) %>%
  arrange(desc(ave)) %>%
  head(1)
```

*Task 2
```{r}
diamonds %>%
  group_by(clarity) %>%
  summarize(ave=mean(table, na.rm=TRUE)) %>%
  arrange(desc(ave)) %>%
  head(1)
```
