# Week 3 Short Answer Questions

## Ruotong Wang

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

**Problem 5.1**
```{r}
library(DataComputing)
ggplot(data=CPS85,aes(x=sex,y=wage,fill=married))+geom_bar(stat='identity',position='dodge')+facet_wrap(~race, ncol = 2)
```

**Problem 5.2**
```{r}
WorldMap(data = HappinessIndex, key = "country", fill = "corruption")
```

**Problem 6.5**
In Figure 6.9, what variables define the frame in this graphic? 
Answer: the x coordinate is the name of the polling organization; y coordinaate is the competitive state. 

**Problem 6.6**
In Figure 6.9, what is the glyph and its graphical attributes?
Answer:d. Glyph: rectange. Graphical attribute: color adn tex. 

**Problem 6.7**
In Figure 6.9, sets the order of the categorical variable in the scale for the vertical variable?
Answer:e. the date of the poll. 

**Problem 6.8**
```{r}
Small <- 
  NCHS %>% 
  sample_n(size=5000)
scatterGraphHelper(Small) 
```
```{r}
ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker) 
```
The bmi value is mapped to x coordinate, weight maps to y coordinate and whether it is a smoker is mapped to the color of each glyph. 

**Problem 7.1**
a)summerise b)mutate c)arrange d)filter e)select f)group_by and summarise 
**Problem 7.4**
a) the text follow the group_by verb should not be put in ""
b) there should not be tmp followed summerise 
c) there should be a chaining sytax followed at the end of the first line
**Problem 7.5**
a)
BabyNames %>% 
  arrange(sex,count)
b)
BabyNames %>% 
  arrange(sex)
c)
BabyNames %>% 
  select(sex=M)
d)
BabyNames %>% 
  summerise(total=sum(count))
**Problem 7.7**
1) BabyNames does not need to appear three times
2) <- should be replaced by %>%
3)-> should be replaced by %>%
4) Minneaplilis 2013 should be put in the first row, before a %>%
**Problem 7.11**
a. sex,count,meanAge
b. diagnosis, count, meanAge
c, sex, diagnosis, count, meanAge
d. age, diagnosis, count, meanAge
f. age, count, meanAge
**Problem 7.12**
1)nrow
2)names
3)help
4)library
5)group_by
6)summarise
